Correlation among smart grid actors

### 2015-07-22 Article.tex
abstract modif

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Abstract
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Achieving a successful energetic transition became a major goal for the 21st century in most developped countries. The reconciliation of several research areas and their recent focus on the same smart grid objective has led to major technical improvements. For instance, allowing a large penetration of renewables into the electricity production grid seemed more like a dream yesterday, but appears more and more doable as research progresses. The inherent volatility of some of these energy sources poses indeed various problems in such a constrained environment. It is often supposed that a large number of these small generators will be decentralized down to the distribution network and even be owned by individuals. By enabling bi-directional flows, this vision revolutionises the nature of today simple consumers into futuristic agents that can both consume and produce. Such agents can obviously reduce their electricity bills by seeking energetic independance through demand side management programs coupled with storage. Nevertheless, as it could be the case that an agent's production exceeds its consumption and storage capacity, its ability to sell its extra-production appears as a way to save energy.

In this paper, we thus consider agents that tend to produce more than they consume and seek to sell their surplus of production. More precisely, we rely on aggregations of these agents that can be seen as virtual power plants with production and consumption components that are both variable. Because these virtual power plants are complex aggregations of different types of production means and consumption habits, the volatilities of the plants productions are deeply impacted by the correlation between the agents. We propose here an algorithm that takes the underlying correlation structure of the agents into account while forming the coalitions. We show then that the resulting diversified coalitions are able to generate higher benefits on a constrained energy market, and are more resilient to random failures of the agents.
\end{abstract}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Abstract
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
%Achieving a successful energetic transition became a major goal for the 21st century in most developped countries. The reconciliation of several research areas and their recent focus on the same smart grid objective has led to major technical improvements. For instance, allowing a large penetration of renewables into the electricity production grid seemed more like a dream yesterday, but appears more and more doable as research progresses. The inherent volatility of some of these energy sources poses indeed various problems in such a constrained environment. It is often supposed that a large number of these small generators will be decentralized down to the distribution network and even be owned by individuals. By enabling bi-directional flows, this vision revolutionises the nature of today simple consumers into futuristic agents that can both consume and produce. Such agents can obviously reduce their electricity bills by seeking energetic independance through demand side management programs coupled with storage. Nevertheless, as it could be the case that an agent's production exceeds its consumption and storage capacity, its ability to sell its extra-production appears as a way to save energy.

Achieving a successful energetic transition through a smarter and greener electricity grid is a major goal for the 21st century. It is assumed that such smart grids will be characterized by bidirectional electricity flows coupled with a large penetration of small renewable generators and a proper efficient information system. All these bricks might enable end users to take part in the grid stability by injecting power, or by shaping their consumption against financial compensation. In this paper, we study the formation of coalitions of these futuristic agents that both produce and consume. These coalitions, which can be seen as aggregators of the electricity market, aim at selling the aggregated surplus of production of the agents they control. We rely on real weather data sampled accross stations of a given territory in order to simulate realistic production and consumption patterns for each agent. This approach enables us to capture geographical correlations among the agents while preserving the diversity due to different behaviors. As aggregators are bound to the grid operator by a contract, they seek to maximize their offer while minimizing their risk. We propose here an algorithm that takes the underlying correlation structure of the agents into account and outputs coalitions with both high productivity and low variability. We show then that the resulting diversified coalitions are able to generate higher benefits on a constrained energy market, and are more resilient to random failures of the agents.
\end{abstract}
